Implementing \Kwd{DNS} in \Kwd{C0}

### 2017-12-14 paper.tex
Small change to wording in evaluation:performance.

Because of the low throughput of our system, we did not find it useful to test directly against commercial nameservers, relying instead on previous work such as \cite{fagin2017making}, which suggests that commercial authoritative nameservers can handle loads on the order of 20,000 to 80,000 queries per second, while (at least some) commercial recursive nameservers behave well up to at least 4000 queries per second (See Figure~\ref{fig:commercial-perf}). With such a large magnitude of difference, even if commercial nameservers perform substantially worse on our benchmark than on the benchmarks that others have used, we still have around 100-200 times less throughput. Additionally, considering latency shows that commercial nameservers tend to have consistent latency once under sufficiently high load, where \Kwd{c0ns}' latency continues to increase with load until it fails to return results within a reasonable amount of time.

>>>>

Because of the low throughput of our system, we did not find it useful to test directly against commercial nameservers, relying instead on previous work such as \cite{fagin2017making}, which suggests that commercial authoritative nameservers can handle loads on the order of 20,000 to 80,000 queries per second, while (at least some) commercial recursive nameservers behave well up to at least 4000 queries per second (See Figure~\ref{fig:commercial-perf}). With such a large magnitude of difference, even if commercial nameservers perform substantially worse on our benchmark than on the benchmarks that others have used, we still have around 100-200 times less throughput than the maximum shown on these graphs. Additionally, considering latency shows that commercial nameservers tend to have consistent latency once under sufficiently high load, where \Kwd{c0ns}' latency continues to increase with load until it fails to return results within a reasonable amount of time.
